TO FIND

### 2013-05-22 ms.tex

>>>>

Finally, fig. 3 and fig. 4 present, respectively, the between patch $\beta$
diversity as a function of the shape of the network, under three dynamic models.
In figure 3, the distance is expressed as the euclidean (geographic) distance
between two patches. Although this neglects how dispersal connects the different
patches, there is already a clear signal of $\beta$ diversity. In both the
neutral and patch dynamics model, local communities become increasingly
dissimilar when the distance between them increases. In other words, two
communities which are close to each other will share a large proportion of their
species, whereas two communities which are afar will share a small proportion.
In the species-sorting model, the relationship between distance and
dissimilarity is similar, Nonetheless, it forms an enveloppe of points (with
most points lying in the upper-left part of the graph). While two distant
communities will be dissimilar, there is no telling how dissimilar two close
communities will be.

To a vast extent, these relationships are preseved when looking at the
topological distances, i.e. along how many edges should one travel to connect
two patchs. Interestingly enough, the distance-dissimilarity relationship for
the neutral model is markedly hump-shaped, with sites being at a medium distance
having the maximal dissimilarity.
